---
title: "R Markdown & Leaflet"
author: "Markos Hay"
data: "10/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is an Coursera project defined as follow= “Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!"

# Required Packages

```{r}
library(leaflet)
```

```{r}
library(htmltools)
```

# Data Plotted

From Kagle: Dataset about the best restaurants in the world. By Megh Mayur. Contains the list of The World’s 50 Best Restaurants for 2018 (https://www.kaggle.com/mmayur/the-worlds-50-best-restaurants)

```{r}
datamap <- read.csv(file = "data.csv", header = TRUE, sep = ",")
```

# Creating Data Frame to read as Table

```{r}
mimapa <- data.frame(Ranking = datamap$Ranking,
                     Name = datamap$Name,
                     City = datamap$City,
                     Country = datamap$Country,
                     Latitude = datamap$Latitude,
                     Longitude = datamap$Longitude
                     )
```

# Map Plot

```{r}
map <- mimapa %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=paste
             ("<br>Country: ", 
               htmlEscape(mimapa$Country), 
              "<br>City: ", 
               htmlEscape(mimapa$City), 
              "<br>Restaurant: ", 
               htmlEscape(mimapa$Name),
              "<br>Ranking: ",
               formatC(datamap$Ranking, format = "d", big.mark = ",")
              ) 
            )
```

```{r}
map
```